% List of changes for QIRT_JOURNAL 2016
\documentclass[letter]{article}

\usepackage{fontspec}

\begin{document}
    
\title{List of changes for QIRT Journal No. TQRT-2016-0033}
\author{Lei Lei}
\date{2017 May 11}

\maketitle


\begin{enumerate}
    \item Change all four different terms of infrared camera into the one "thermal camera"
    \item Page 1, line 22: "infrared" instead of "Infrared"
    \item Page 1, line 28/29: capitalize none of the key words.
    \item Page 2, line 46: write all nouns with lower cases 
    \item Page 2, line 59: add a blank between each number and the unit (1000 W instead of 1000W) 
    \item Page 3, line 21: write "set-up" instead of "Set-up"
    \item Page 3, line 30, 34, 38: add a blank between each number and the unit 
    \item Page 3, line 30: write "zoomed" instead of "Zoomed"
    \item Page 4, line 9: move the "3" to the exponent.
    \item Page 4, line 11: add the unit of time 
    \item Page 4, line 21: write "room" instead of "Room"
    \item Page 4, line 49: use lower cases.
    \item Page 5, line 8: write "thermal bridge" instead of "Thermal bridge"
    \item Page 5, line 19: write "front view" instead of "Front View"
    \item Page 5, line 23: write "thermal bridge" instead of "Thermal bridge"
    \item Page 5, line 42: write "a uniform" instead of "an uniform"
    \item Page 5, line 53 to 55: use lower capitals for all words.
    \item Page 5, line 60: write "(the descendant" instead of "(The descendant"
    \item Page 5: Figure 5: use lower capitals in all captions.
    \item Page 6: Figure 6: use lower capitals in all captions. use the same sizes of the captions in all diagrams.
    \item Page 6, line 43: write "lamp heating" instead of "Lamp Heating"
    \item Page 6, line 53/54/55: use lower cases for all nouns.
    \item Page 7: Figure 7: use lower capitals in all captions.
    \item Page 9, line 15 to 17: use lower cases for all nouns.
    \item Page 10, Ref. 8: add the report number  DSTO-TR-1298.

\end{enumerate}

\end{document}
